\subsection{Fine-Tuned Transformer Model (BERT-base-uncased)}
This model, BERT-base-uncased, is a pretrained transformer encoder model that is fine-tuned to multi-class sequence classification. A classification head was added on top of the token representation to predict on of the several possible movie genres. 

To implement this model, dataset was first converted into a Hugging Face Dataset object, and genre labels were mapped to integer IDs using a ClassLabel feature. After that, the data was tokenized and split into a training and validation/test set using an 80/20 split. 

The training for the model was conducted using Hugging Face’s ‘Trainer’ API with configurations such as, a learning rate of 2e-5, a batch size of 8, 3 epochs, and an evaluation strategy of choosing the best model of the 3 epochs. The selection and performance for this was measured using accuracy and weighted F1 scores. The final model achieved an accuracy score of 0.5586 and a weighted F1 score of 0.5319. 

To evaluate overall performance, the two majority and random baselines were used. The BERT significantly outperformed both and demonstrated its ability to learn meaningful patterns from the data.

One challenge with for model is the fact that the task is single-label classification. Movies can often belong to several different genres and limiting to a single label likely limits performance of the model. Additionally, for timing purposes, there was limited hyperparameter tuning, likely preventing the model from reaching optimal performance. 

For more details, model used (BERT-base-uncased), is cited at the end of this report.
